Performance-portable Parallel Programming in Computer Science Education with Kokkos

### 2020-01-23 src/2.GenericProgramming.tex
Stab at point one of the "semantic capture" point

Semantic information provided by the programmer to the parallel programming model can be grouped into information to express intent and properties. They address the question of \emph{what}, \emph{where} and \emph{how}. In the context of parallel programming, these correspond to defining which code portion to parallelize, where to run and access and how to run that parallel code. Synchronization primitives may be considered as part of the what and information on the execution properties such as data placement or memory access type as the how. Semantics are expressed following a paradigm and a programming language.

>>>>

%Semantic information provided by the programmer to the parallel programming model can be grouped into information to express intent and properties. They address the question of \emph{what}, \emph{where} and \emph{how}. In the context of parallel programming, these correspond to defining which code portion to parallelize, where to run and access and how to run that parallel code. Synchronization primitives may be considered as part of the what and information on the execution properties such as data placement or memory access type as the how. Semantics are expressed following a paradigm and a programming language.

To enable developers to achieve performance portability, we needed to constrain what intent they could specify to Kokkos. We settled on Kokkos supporting semantics for offloading loops, the allocation and freeing of data, and data movement. Critically, we decided against exposing machine details to the developer, we aim to increase portability of code by only exposing an abstract execution model (described later) to the users. Our semantics map naturally to C-like languages, with malloc/new calls replaced with the construction and destruction of abstract data types, and many loop types replaced with corresponding parallel patterns. This clean mapping between traditional C-like semantics and our model came from requirements from our physics teams, but also makes Kokkos a good choice for students as it will more closely track with what they've seen before.

%TODO DZP: keep going here
